Visualization of [fulle name] Fractional Integrals

### 2019-04-25 fractional/CMJ style files/article-template.tex
improved description

Let us first consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}. We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
the above integral into a Riemann-Stieltjes integral:
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
\end{equation}
We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
\begin{equation}
\label{eq:ex1}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
\end{equation}
We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau. 
\end{equation}
This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
this region with the symbol $R_{10}^{\frac{4}{5}}$. The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. We are now in a position to assign a geometric 
interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$
by summing together the area of non-rectangular integration strips that inscribe $R_{10}^{\frac{4}{5}}$. The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five integration strips of equal width. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.

>>>>

Let us first consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}. We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
the above integral into a Riemann-Stieltjes integral:
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
\end{equation}
We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
\begin{equation}
\label{eq:ex1}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
\end{equation}

We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
they depend on the value of $\alpha$ and $t$. This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. We are now in a position to assign a geometric 
interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$ by summing together the area of $n$ non-rectangular integration strips of the same width that inscribe $R_{10}^{\frac{4}{5}}$. The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}. The sides of the 
aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines. Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
Eq??, i.e. the area of $R_{10}^{\frac{4}{5}}$.

In the limit this sum approaches the area of $R_{10}^{\frac{4}{5}}$

In general can use $n$ integration strips to approximate 
the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
the area of $R_{10}^{\frac{4}{5}}$.

Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five non-rectangualr integration strips of equal width. Mathematically speaking, this is accomplished 
by setting $n$ to 5 in Eq??. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.
